Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-04-06 summary.Rmd
updated clustering simulations to have both EP and louvain

```{r clust_err_k, fig.cap = 'IQR of clustering error using OSC (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are approximately balanced. Simulations were repeated 50 times for each sample size.', fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error rate', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm, ymax = third.q.mm,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2, ymax = third.q.ssc2,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

@@

```{r clust_err_ct_sim, fig.cap = 'IQR of counts of misclustered vertices using OSC (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are approximately balanced. Simulations were repeated 50 times for each sample size.', cache = FALSE, fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(med.err = median(error),
                   first.q = quantile(error, .25),
                   third.q = quantile(error, .75),
                   med.err.ssc = median(error.ssc),
                   first.q.ssc = quantile(error.ssc, .25),
                   third.q.ssc = quantile(error.ssc, .75),
                   med.err.mm = median(error.mm),
                   first.q.mm = quantile(error.mm, .25),
                   third.q.mm = quantile(error.mm, .75)) %>%
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error count', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err * n,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q * n, ymax = third.q * n,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc * n,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc * n, ymax = third.q.ssc * n,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.mm * n,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.mm * n, ymax = third.q.mm * n,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2 * n,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2 * n, ymax = third.q.ssc2 * n,
                    colour = 'SSC-A'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

>>>>

```{r clust_err_k, fig.cap = 'IQR of clustering error using OSC (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are approximately balanced. Simulations were repeated 50 times for each sample size.', fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(
    med.err = median(error),
    first.q = quantile(error, .25),
    third.q = quantile(error, .75),
    med.err.ssc = median(error.ssc),
    first.q.ssc = quantile(error.ssc, .25),
    third.q.ssc = quantile(error.ssc, .75),
    med.err.ep = median(error.ep, na.rm = TRUE),
    first.q.ep = quantile(error.ep, .25, na.rm = TRUE),
    third.q.ep = quantile(error.ep, .75, na.rm = TRUE),
    med.err.louvain = median(error.louvain),
    first.q.louvain = quantile(error.louvain, .25),
    third.q.louvain = quantile(error.louvain, .75)
  ) %>% 
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error rate', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q, ymax = third.q,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc, ymax = third.q.ssc,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ep,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ep, ymax = third.q.ep,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2, ymax = third.q.ssc2,
                    colour = 'SSC-A'), width = .1) + 
  geom_line(aes(x = n, y = med.err.louvain,
                colour = 'MM-Louvain')) + 
  geom_errorbar(aes(x = n, ymin = first.q.louvain, ymax = third.q.louvain,
                    colour = 'MM-Louvain'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```

@@

```{r clust_err_ct_sim, fig.cap = 'IQR of counts of misclustered vertices using OSC (blue) compared against SSC on the ASE of A (purple), MM (red), and SSC on the adjacency matrix (green). Communities are approximately balanced. Simulations were repeated 50 times for each sample size.', cache = FALSE, fig.width = 10}
clustering.df <- readr::read_csv('clustering-k.csv')
ssc.df <- readr::read_csv('clustering-ssc-k.csv')
clustering.df %>%
  dplyr::group_by(n, K) %>%
  dplyr::summarise(
    med.err = median(error),
    first.q = quantile(error, .25),
    third.q = quantile(error, .75),
    med.err.ssc = median(error.ssc),
    first.q.ssc = quantile(error.ssc, .25),
    third.q.ssc = quantile(error.ssc, .75),
    med.err.ep = median(error.ep, na.rm = TRUE),
    first.q.ep = quantile(error.ep, .25, na.rm = TRUE),
    third.q.ep = quantile(error.ep, .75, na.rm = TRUE),
    med.err.louvain = median(error.louvain),
    first.q.louvain = quantile(error.louvain, .25),
    third.q.louvain = quantile(error.louvain, .75)
  ) %>% 
  dplyr::ungroup() %>% 
  dplyr::inner_join(
    ssc.df %>% 
      dplyr::group_by(n, K) %>% 
      dplyr::summarise(med.err.ssc2 = median(error.ssc2),
                       first.q.ssc2 = quantile(error.ssc2, .25),
                       third.q.ssc2 = quantile(error.ssc2, .75)) %>% 
      dplyr::ungroup()
  ) %>% 
  ggplot() +
  scale_x_log10(breaks = c(128, 256, 512, 1024, 2048, 4096)) +
  # scale_x_continuous(breaks = c(128, 256, 512, 1024, 2048, 4096)) + 
  labs(y = 'community detection error count', 
       colour = NULL) +
  geom_line(aes(x = n, y = med.err * n,
                colour = 'OSC')) +
  geom_errorbar(aes(x = n, ymin = first.q * n, ymax = third.q * n,
                    colour = 'OSC'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc * n,
                colour = 'SSC-ASE')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc * n, ymax = third.q.ssc * n,
                    colour = 'SSC-ASE'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ep * n,
                colour = 'MM-EP')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ep * n, ymax = third.q.ep * n,
                    colour = 'MM-EP'), width = .1) + 
  geom_line(aes(x = n, y = med.err.ssc2 * n,
                colour = 'SSC-A')) + 
  geom_errorbar(aes(x = n, ymin = first.q.ssc2 * n, ymax = third.q.ssc2 * n,
                    colour = 'SSC-A'), width = .1) + 
  geom_line(aes(x = n, y = med.err.louvain * n,
                colour = 'MM-Louvain')) + 
  geom_errorbar(aes(x = n, 
                    ymin = first.q.louvain * n, ymax = third.q.louvain * n,
                    colour = 'MM-Louvain'), width = .1) + 
  scale_colour_brewer(palette = 'Set1') + 
  facet_wrap(~ K, labeller = 'label_both') + 
  scale_y_log10()
```
